\item k31r - Original rank: 23. Authored by Gail Grisell
\item k32r - Original rank: 10. Authored by Charles Kluepfel
\item k33r - Original rank: 59. Authored by Harold Rabbie
\item k34r - Original rank: 52. Authored by James W Friedman
\item k35r - Original rank: 11. Authored by Abraham Getzler
\item k36r - Original rank: 63. Authored by Roger Hotz
\item k37r - Original rank: 37. Authored by George Lefevre
\item k38r - Original rank: 34. Authored by Nelson Weiderman
\item k39r - Original rank: 25. Authored by Tom Almy
\item k40r - Original rank: 35. Authored by Robert Adams
\item k41r - Original rank: 7. Authored by Herb Weiner
\item k42r - Original rank: 3. Authored by Otto Borufsen
\item k43r - Original rank: 39. Authored by R D Anderson
\item k44r - Original rank: 5. Authored by William Adams
\item k45r - Original rank: 50. Authored by Michael F McGurrin
\item k46r - Original rank: 14. Authored by Graham J Eatherley
\item k47r - Original rank: 16. Authored by Richard Hufford
\item k48r - Original rank: 53. Authored by George Hufford
\item k49r - Original rank: 4. Authored by Rob Cave
\item k50r - Original rank: 54. Authored by Rik Smoody
\item k51r - Original rank: 18. Authored by John William Colbert
\item k52r - Original rank: 48. Authored by David A Smith
\item k53r - Original rank: 45. Authored by Henry Nussbacher
\item k54r - Original rank: 58. Authored by William H Robertson
\item k55r - Original rank: 42. Authored by Steve Newman
\item k56r - Original rank: 38. Authored by Stanley F Quayle
\item k57r - Original rank: 31. Authored by Rudy Nydegger
\item k58r - Original rank: 21. Authored by Glen Rowsam
\item k59r - Original rank: 40. Authored by Leslie Downing
\item k60r - Original rank: 6. Authored by Jim Graaskamp and Ken Katzen
\item k61r - Original rank: 2. Authored by Danny C Champion
\item k62r - Original rank: 51. Authored by Howard R Hollander
\item k63r - Original rank: 57. Authored by George Duisman
\item k64r - Original rank: 17. Authored by Brian Yamachi
\item k65r - Original rank: 47. Authored by Mark F Batell
\item k66r - Original rank: 20. Authored by Ray Mikkelson
\item k67r - Original rank: 27. Authored by Craig Feathers
\item k68r - Original rank: 12. Authored by Fransois Leyvraz
\item k69r - Original rank: 29. Authored by Johann Joss
\item k70r - Original rank: 32. Authored by Robert Pebly
\item k71r - Original rank: 60. Authored by James E Hall
\item k72r - Original rank: 13. Authored by Edward C White Jr
\item k73r - Original rank: 41. Authored by George Zimmerman
\item k74r - Original rank: 61. Authored by Edward Friedland
\item k75r - Original rank: 8. Authored by Paul D Harrington
\item k76r - Original rank: 46. Authored by David Gladstein
\item k77r - Original rank: 55. Authored by Scott Feld
\item k78r - Original rank: 19. Authored by Fred Mauk
\item k79r - Original rank: 26. Authored by Dennis Ambuehl and Kevin Hickey
\item k80r - Original rank: 36. Authored by Robyn M Dawes and Mark Batell
\item k81r - Original rank: 43. Authored by Martyn Jones
\item k82r - Original rank: 49. Authored by Robert A Leyland
\item k83r - Original rank: 15. Authored by Paul E Black
\item k84r - Original rank: 9. Authored by T Nicolaus Tideman and Paula Chieruzz
\item k85r - Original rank: 33. Authored by Robert B Falk and James M Langsted
\item k86r - Original rank: 28. Authored by Bernard Grofman
\item k87r - Original rank: 44. Authored by E E H Schurmann
\item k88r - Original rank: 22. Authored by Scott Appold
\item k89r - Original rank: 56. Authored by Gene Snodgrass
\item k90r - Original rank: 24. Authored by John Maynard Smith
\item k91r - Original rank: 30. Authored by Jonathan Pinkley
\item k92r - Original rank: 1. Authored by Anatol Rapoport
\item krandomc - Original rank: 62. Authored by None
